ICBEdataset figure Metro Maps

### 2022-01-21 README.Rmd
paper start

### ICBe prep
- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates [available online](https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit#gid=0) and  ./data/icb_manual_recording_master_sheet.xlsx
  + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
- [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)

>>>>

### ICBe prep
- Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates (./data/icb_manual_recording_master_sheet.xlsx)
  + actor_translator to compare actors across different datasets, created by hand with assistance from [07_actor_dictionaries](https://centerforpeaceandsecuritystudies.github.io/ICBEdataset/07_actor_dictionaries.html).
- [Lit review and tree/leaf codebook](https://docs.google.com/spreadsheets/d/10tZGzjYgmvrbgQTV3oadVEV8m1LxLEDJEq9pzqq90Fc/edit#gid=1604363724)

### 2022-01-21 replication_data/rmd/02_format_and_clean.rmd
paper start

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
```

>>>>

Save icb_long_clean!
```{r}
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))
saveRDS(icb_long_clean_final, paste0(here::here(), "/replication_paper/data/input/icb_long_clean.Rds"))

### 2022-01-21 replication_data/rmd/03_aggregation.Rmd
paper start

saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds"))

saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))

>>>>

saveRDS(codings_long, paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
saveRDS(codings_long, paste0(here::here(), "/replication_paper/data/in/codings_long.Rds"))

saveRDS(codings_long_agreement, paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds")) 
saveRDS(codings_long_agreement, paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds"))

saveRDS(codings_long_agreed, paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
saveRDS(codings_long_agreed, paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds"))

saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds")) 
saveRDS(codings_wide_agreed_pruned_labeled, paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))

### 2022-01-21 replication_paper/rmd/CaseStudy196.Rmd
paper start

CaseStudy196 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy196")

@@

CaseStudy196_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy196_ft.Rds'))

>>>>

```{r, echo=F, results='asis', message=F, warning=F, eval=T , cache=F}
CaseStudy196 <- readxl::read_excel(paste0(here::here(),"/replication_paper/data/in/CaseStudies.xlsx"), sheet="CaseStudy196")

@@

CaseStudy196_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))

### 2022-01-21 replication_paper/rmd/CaseStudy426.Rmd
paper start

CaseStudy426 <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1lnFqrnCwjWWd_rdWLVHGkxSEcFpw-5XrV7MiQ6rA7KY/edit?usp=sharing", sheet="CaseStudy426")

@@

CaseStudy426_ft  %>% saveRDS(paste0(here::here(), '/paper/tables/CaseStudy426_ft.Rds'))

>>>>

CaseStudy426 <- readxl::read_excel(paste0(here::here(),"/replication_paper/data/in/CaseStudies.xlsx"), sheet="CaseStudy426")

@@

CaseStudy426_ft  %>% saveRDS(paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))

### 2022-01-21 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
paper start

---
title: "Metro Maps"
output: html_document
---

@@

icb_crises <- read.csv(paste0(here::here(), "/replication_data/in/icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_data/temp/icb_long_clean.Rds"))

@@

target_file <- paste0(here::here(),"/replication_data/in/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)

@@

codings_long <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_data/temp/codings_long_agreement.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_long_agreed.Rds")) 
codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_data/out/codings_wide_agreed.Rds"))

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/paper/figures/metro_plots/p_metro_plot_",crisis,".Rds")

@@

    #Units
  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here, '/paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*10)

@@

  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here(), "/paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*5)

@@

icb_sentence_tables <- function(crisis=196){
  print(crisis)
  ft_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")

@@

midip <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDIP_5.01.csv'))

midii <- read_csv(paste0(here::here(), '/data_other_datasets/mids_incidents/MIDI_5.01.csv'))

@@

  print(crisis)
  #crisis=426
  save_mids_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")

@@

icbdy_20 <- read_tsv(here::here(), "/data_other_datasets/icb_dyad/icbdy_20.dat")

@@

icb2v14 <- read_csv(here::here(), "/data_other_datasets/icb/icb2v14.csv")

@@

    print(crisis)
    save_icb_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")

@@

ged211 <- read_csv(here::here(), "/data_other_datasets/ucdp_ged/ged211.csv")

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

    print(crisis)
    #crisis=426
    save_ucdp_incidents_file <- paste0(here::here(), "/paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")

@@

CAMEO_eventcodes <- read_tsv(here::here(), "/data_other_datasets/icews/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()

@@

#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_temp/CAMEO.eventcodes.txt")) %>% janitor::clean_names()

@@

files <- list.files(path = paste0(here::here(), "/data_other_datasets/icews/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
dim(icews)

CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/data_other_datasets/icews/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()

@@

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

  print(crisis)
  #crisis=426
  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
  #save_icews_file = paste0(here::here(), "/paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  if(is.null(savefile)){
    save_icews_file <- paste0(here::here(), "/paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
  }

@@

a <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
b  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
c  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
d  <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
e <- read_csv(paste0(here::here, '/data_other_datasets/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_phoenix_file <- paste0(here::here(), "/paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")

@@

files <- list.files(path = paste0(here::here(), "/data_other_datasets/terrier/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/data_other_datasets/terrier/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
#codes_used <-terrier_clean %>% count(cameo_code)

target_file <- paste0(here::here(),"/data/icb_manual_recoding_master_sheet.xlsx")
downloaded_file <- googledrive::drive_download(file="https://docs.google.com/spreadsheets/d/1a7Id0Zg41PTKEv74H_KjiJzhMak2jGh0leT7B8oVWdI/edit?usp=sharing", path=target_file, type = "xlsx", overwrite=T)
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_terrier_file <- paste0(here::here(), "/paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")

>>>>

---
title: "ICBEdataset figure Metro Maps"
output: html_document
---

@@

icb_crises <- read.csv(paste0(here::here(), "/replication_paper/data/in/icb1v14.csv")) 
#icb_crises <-readRDS(paste0(here::here(), "/data/icb1v14.Rds") )

icb_long_clean <- readRDS(file=paste0(here::here(), "/replication_paper/data/in/icb_long_clean.Rds"))

@@

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")

@@

codings_long <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long.Rds")) 
codings_long_agreement <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreement.Rds")) 
codings_long_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_long_agreed.Rds")) 
codings_wide_agreed <- readRDS( paste0(here::here(), "/replication_paper/data/in/codings_wide_agreed.Rds"))

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_metro_plot_", crisis, ".Rds")

@@

    #Units
  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here, '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*10)

@@

  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here(), "/replication_paper/figures/metro_plots/symbols/",interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*5)

@@

icb_sentence_tables <- function(crisis=196){
  print(crisis)
  ft_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_file <- paste0(here::here(), "/replication_paper/tables/sentence_tables/ft_sentence_table_",crisis,".Rds")

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_mids_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_metro_plot_",crisis,".Rds")

@@

midip <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDIP_5.01.csv'))

midii <- read_csv(paste0(here::here(), '/replication_paper/data/in/MIDI_5.01.csv'))

@@

  print(crisis)
  #crisis=426
  save_mids_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_mids_incidents_metro_plot_",crisis,".Rds")

@@

icbdy_20 <- read_tsv(here::here(), "/replication_paper/data/in/icbdy_20.dat")

@@

icb2v14 <- read_csv(here::here(), "/replication_paper/data/in/icb2v14.csv")

@@

    print(crisis)
    save_icb_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icb_metro_plot_",crisis,".Rds")

@@

ged211 <- read_csv(here::here(), "/replication_paper/data/in/ucdp_ged/ged211.csv")

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

    print(crisis)
    #crisis=426
    save_ucdp_incidents_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_ucdp_metro_plot_",crisis,".Rds")

@@

CAMEO_eventcodes <- read_tsv(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt", col_types='cc') %>% janitor::clean_names()

@@

#CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt")) %>% janitor::clean_names()

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/dataverse_files (1)/"), pattern = ".tab$", full.names = T)
icews <- bind_rows(lapply(files, FUN=function(x) read_tsv(x) )  ) %>% janitor::clean_names()
dim(icews)

CAMEO_eventcodes <- read_tsv(paste0(here::here(),"/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc') %>% janitor::clean_names()

@@

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

  print(crisis)
  #crisis=426
  #exclude = c('Chad', 'Southern African Development Community','United States','European Union','South Africa','Zambia','Namibia', 'Angola','United Nations','Zimbabwe')
  #save_icews_file = paste0(here::here(), "/replication_paper/figures/p_icews_metro_plot_",crisis,"_paper.Rds")
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  if(is.null(savefile)){
    save_icews_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_icews_metro_plot_",crisis,".Rds")
  }

@@

a <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-NYT_1980-2018.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
b  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixBLN-SWB_1979-2019.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
c  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixFBIS_1995-2004.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
d  <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixNYT_1945-2005.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))
e <- read_csv(paste0(here::here, '/replication_paper/data/in/phoenix/PhoenixWSJ_1945-2006.csv', col_types = 'ccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc'))

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_phoenix_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_phoenix_metro_plot_",crisis,".Rds")

@@

files <- list.files(path = paste0(here::here(), "/replication_paper/data/in/largegeolocateddata/"), pattern = ".tsv$", full.names = T)
terrier <- bind_rows(lapply(files, FUN=function(x) read_tsv(x,col_names=F, col_types=paste0(rep('c',50), collapse='')  )  ) ) %>% janitor::clean_names()
dim(terrier) #28,370,448       28

CAMEO_eventcodes <- read_tsv(paste0(here::here(), "/replication_paper/data/in/CAMEO.eventcodes.txt"), col_types='cc' ) %>% janitor::clean_names()
#codes_used <-terrier_clean %>% count(cameo_code)

target_file <- paste0(here::here(),"/replication_paper/data/in/icb_manual_recoding_master_sheet.xlsx")
actor_translator    <- readxl::read_excel(target_file, sheet="actor_translator")

@@

  print(crisis)
  #crisis=426
  plot_title <- crisno_name_years %>% filter(crisno==crisis) %>% mutate(title="Crisis #" %>% paste0(crisno, " ", crisname, " (", yrtrig, "-",yrterm,")")) %>% pull(title)
  save_terrier_file <- paste0(here::here(), "/replication_paper/figures/metro_plots/p_terrier_metro_plot_",crisis,".Rds")
